---
title: "Forest plots for brmsfit models with varying effects"
author: "Matti Vuorre"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r packages, message = F}
library(here)
library(brms)
library(brmstools)
library(dplyr)
```

# Introduction

Forest plots display estimated parameters from multiple sources (studies, participants, etc.) in one figure. They are most commonly used in meta-analysis, where individual studies are used to inform an average, or meta-analytic, overall estimate. However, they can be seamlessly applied to other types of multilevel models--models in which parameters are assumed to vary among units. **brmstools**' `forest()` function draws forest plots from `brmsfit` objects. They should be most useful for meta-analytic models, but can be produced from any `brmsfit` with one or more varying parameters.

The `forest()` function uses the fantastic [ggridges R package](https://github.com/clauswilke/ggridges) in the backend, and assumes you've installed it. If you haven't, `forest()` will return an error.

# Random effects meta-analysis

We illustrate using a data set from the metafor package.

```{r}
data("dat.bangertdrowns2004", package = "metafor")
dat <- dat.bangertdrowns2004 %>%
  mutate(study = paste0(author, " (", year, ")"), sei = sqrt(vi)) %>%
  select(study, yi, sei) %>%
  slice(1:15)
```

brms allows flexible specification of meta-analytic models.

```{r, eval = F}
fit_rem <- brm(
  yi | se(sei) ~ 1 + (1|study),
  data = dat,
  cores = 4, 
  control=list(adapt_delta = .99)
)
```

```{r, eval = F, echo=F}
# Save time by using locally saved models
save(fit_rem, file = here("vignettes/forest-plots/fit_rem.rda"))
```

```{r, echo = F}
load(here("vignettes/forest-plots/fit_rem.rda"))
```

Use `forest()` to draw the forest plot:

```{r}
forest(fit_rem)
```

There are various options (see `?forest`)

```{r}
forest(fit_rem, 
       level = .80, 
       av_name = "Meta-Analytic\nEstimate", 
       col_ridge = "purple", 
       fill_ridge = "grey90")
```

Data points can also be shown (note this probably only makes sense with a meta-analytic model):

```{r}
forest(fit_rem, show_data = T)
```

# Multilevel model

The `forest()` function can be seamlessly applied to any multilevel model. 

We use example data from the lme4 package.

```{r}
data(sleepstudy, package = "lme4")
head(sleepstudy)
```

A multilevel model with varying intercepts and slopes (effect of `Days`):

```{r, eval = F}
fit_ml <- brm(
  Reaction ~ Days + (Days|Subject),
  data = sleepstudy,
  cores = 4
)
```

```{r, eval = F, echo = F}
save(fit_ml, file = here("vignettes/forest-plots/fit_ml.rda"))
```

```{r, echo = F}
load(here("vignettes/forest-plots/fit_ml.rda"))
```

If there are multiple varying parameters, users can input a variable name:

```{r}
forest(fit_ml, pars = "Days")
```

Or let the function automatically draw a plot with all the variables:

```{r}
forest(fit_ml, digits=0)
```

You can also turn off the ridgeline plots (densities)

```{r}
forest(fit_ml, density = F, digits=0)
```

