---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# brmstools

brmstools is an R package [available on GitHub](https://github.com/mvuorre/brmstools). 

brmstools provides convenient plotting and post-processing functions for brmsfit objects (bayesian regression models fitted with the [brms R package](https://github.com/paul-buerkner/brms)). 

brmstools is in beta version so will probably break down with some inputs: [Suggestions for improvements and bug reports](https://github.com/mvuorre/brmstools/issues) are welcomed. For anything more complex I strongly recommend using brms' native functions instead (particularly its `marginal_effects()` and `hypothesis()` methods. Combined with ggplot2 those functions will create any visualization you can think of.)

# Install brmstools

Install brmstools from GitHub with [devtools](https://cran.r-project.org/package=devtools):

```{r, eval = F}
# install.packages("devtools")
devtools::install_github("mvuorre/brmstools")
```

Loading brmstools also loads the brms package:

```{r}
library(brmstools)
```

# Forest plots

Notably, `forest()` draws forest plots for meta-analytic and multilevel models:

```{r forest, echo=-1}
load(here::here("vignettes/forest-plots/fit_rem.rda"))
forest(fit_rem)
```

# Panel plots

`panels()` draws panel plots:

```{r panels, echo=-1}
load(here::here("vignettes/forest-plots/fit_ml.rda"))
panels(fit_ml, xvar = "Days")
```

# Spaghetti plots

`spaghetti()` draws spaghetti plots:

```{r spaghetti}
spaghetti(fit_ml, xvar = "Days")
```

# Coefficient plots

`coefplot()` draws coefficient plots:

```{r}
coefplot(fit_ml)
```

# More information

Examples and instructions can be found at <https://mvuorre.github.io/brmstools>.

