---
title: "Panel and spaghetti plots"
author: "Matti Vuorre"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r packages, message = F}
library(here)
library(brms)
library(brmstools)
library(dplyr)
```

# Panel plot

A panel plot displays each units data along with the model's fitted values. Currently, the function only supports models with one predictor variable.

```{r, echo = F}
load(here("vignettes/forest-plots/fit_ml.rda"))
```

These functions rely on obtaining tidy tibbles of the model's fitted values:

```{r}
tidyfitted(fit_ml)
```

Use `panels()` by setting a variable to be drawn on the x-axis (`xvar`), and (optional) parameter to sort the panels by:

```{r}
panels(fit_ml, xvar = "Days", sort = "Days")
```

Show data as points with `panels(..., data = T):

```{r}
panels(fit_ml, xvar = "Days", sort = "Days", data = T)
```

There are other options (see `?panels`):

```{r}
panels(fit_ml, 
       xvar = "Days", 
       ribbon_fill = NA, 
       ribbon_col = "black")
```

# Spaghetti plots

A spaghetti plot displays regression lines of all levels of the grouping factor in a single panel.

```{r}
spaghetti(fit_ml, xvar = "Days")
```

